---
title: "Installing `discent`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Installing `discent`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## From Github 
```{r, eval=F}
install.packages("remotes")
remotes::install_github("nickbrazeau/discent")
```

### Dependencies
`discent` relies on the [Rcpp](https://cran.r-project.org/web/packages/Rcpp/index.html) package, which requires certain OS-specific dependencies: 

* Windows
    - Download and install the appropriate version of [Rtools](https://cran.rstudio.com/bin/windows/Rtools/) for your version of R. On installation, ensure you check the box to arrange your system PATH as recommended by Rtools
* Mac OS X
    - Download and install [XCode](http://itunes.apple.com/us/app/xcode/id497799835?mt=12)
    - Within XCode go to Preferences : Downloads and install the Command Line Tools
* Linux (Debian/Ubuntu)
    - Install the core software development utilities required for R package development as well as LaTeX by executing
    ```
    sudo apt-get install r-base-dev texlive-full
    ```

Assuming everything installed correctly, you can now load the package:

```{r, eval=F}
library(discent)
```
